---
title: "Logistic Regression with Kickstarter Data - Seasons"
author: "Marcelo Sanches"
date: "August 23, 2018"
output: pdf_document
---

# Project Overview and Limitations

This project is a continuation of Project No.1, so the scope and limitations of that project apply. See full description in the Project No. 1 files.

This project focuses on seasonal aspects of kickstarter projects.


# 1. Data Cleaning and Preparation


The data cleaning process is the same up until the creation of dummy variables for the main categories. 
We do not use kickstarter main categories in this project so we dump that variable. 

``` {r eval=TRUE, echo=FALSE, out.width='70%'}
# load pertinent variables 
ks18 <- read.csv(file = "./kickstarter data/ks-projects-201801.csv", header = TRUE)[,-c(1:3, 5, 9, 11, 13:15)]

# subset US projects, remove country variable 
us18 <- ks18[ks18$country == "US", -6]

# remove "live" projects (no outcome to base prediction on)
us18 <- us18[us18$state != "live", ]

# convert factors to date variables 
us18$deadline <- as.Date(us18$deadline)  
us18$launched <- as.Date(us18$launched)

# compute duration (project length) variable 
us18$duration <- as.numeric(us18$deadline - us18$launched)

# re-order data 
us18 <- us18[,c(5,4,2,6,3,1)]

# dummy-code outcome variable 'state' to predict success 
us18$state <- ifelse(us18$state == "successful", 1, 0)

# discard senseless date outliers (projects from 1970) 
us18 <- us18[us18$duration < 100, ]

# discard projects under $100 --> gaming the system
us18 <- us18[us18$goal > 99, ]

# transform goal distribution to log(log(goal)) so as to normalize it for regression 
us18$logloggoal <- log(log(us18$goal))

# dump goal and main_category 
us18 <- us18[, -c(5,6)]
head(us18)
```

To create seasons out of the launched and deadline dates, I've re-formatted the `getSeason` function created by Josh O'Brien in [**this 2012 StackOverflow post**](https://stackoverflow.com/questions/9500114/find-which-season-a-particular-date-belongs-to).
(See code appendix for details.)

``` {r eval=TRUE, echo=FALSE, out.width='70%'}
# recode dates as seasons  
# getSeason function (from 2012 StackOverflow post by Josh O'Brien)
getSeason <- function(DATES) {
    WS <- as.Date("2012-12-21", format = "%Y-%m-%d") # Winter Solstice
    SE <- as.Date("2012-3-21",  format = "%Y-%m-%d") # Spring Equinox
    SS <- as.Date("2012-6-21",  format = "%Y-%m-%d") # Summer Solstice
    FE <- as.Date("2012-9-21",  format = "%Y-%m-%d") # Fall Equinox

    # Convert dates from any year to 2012 dates
    d <- as.Date(strftime(DATES, format="2012-%m-%d"))

    ifelse (d >= WS | d < SE, "Winter",
      ifelse (d >= SE & d < SS, "Spring",
        ifelse (d >= SS & d < FE, "Summer", "Fall")))
}

# pass us18 date variables to getSeason
us18$launched <- getSeason(us18$launched)
us18$deadline <- getSeason(us18$deadline)
head(us18)
```

``` {r eval=TRUE, echo=TRUE}
# percentage of different seasons for launched and deadline 
round(nrow(us18[us18$launched != us18$deadline, ])/nrow(us18),4)*100
```

We see that $37\%$ of the time the launched and deadline dates fall into different seasons. 
Several avenues of thought could be pursued:

- Use launched dates: campaign efforts tend to skew toward the beginning of a project 
- Use deadline dates: compare with launched dates 
- Create a season variable using a more fine-toothed comb: if a project mostly happened during one season, re-code it for that season 
- Dump all the ambiguous projects: speedy results 

We could also reorient the analysis toward a particular date and compute project success as a function of how far from that date a project was launched or met the deadline.

As a first quick attempt, we dump all the ambiguous projects, since even after $37\%$ of the data is gone we still have $181,464$ rows. Then we create dummy variables for K-1 seasons (base case = Fall).

``` {r eval=TRUE, echo=FALSE, out.width='70%'}
# dump 37% of the data with ambiguous seasons 
seasonmatch <- us18[us18$launched == us18$deadline, -2]

# dummies for seasons, base case == Fall 
seasonmatch$winter <- ifelse(seasonmatch$deadline == "Winter", 1, 0)
seasonmatch$spring <- ifelse(seasonmatch$deadline == "Spring", 1, 0)
seasonmatch$summer <- ifelse(seasonmatch$deadline == "Summer", 1, 0)

# dump deadline
seasonmatch <- seasonmatch[, -2]
head(seasonmatch)
```


---



# 2. Data Analysis 

We use a logistic regression model with an interaction between duration and goal.

``` {r eval=TRUE, echo=FALSE, out.width='70%'}
# logistic regression call 
mod1 <- glm(state ~ duration * logloggoal + winter + spring + summer,
			family=binomial, 
			data=seasonmatch)
summary(mod1)
```

```

```

We then calculate prediction probabilities for plotting, which required many lines of code, found in the appendix. 

``` {r eval=TRUE, echo=FALSE, out.width='70%'}
# a0 coef means Film & Video project with 0-day duration and $0 logloggoal 
a0 <- coef(mod1)[1] 
b_duration <- coef(mod1)[2]
b_logloggoal <- coef(mod1)[3]
b_winter <- coef(mod1)[4]
b_spring <- coef(mod1)[5]
b_summer <- coef(mod1)[6]
b_interaction <- coef(mod1)[7]


# PREDICTIONS
# initial values for loops 
durations <- 92
loglogGOAL1 <- log(log(100))
loglogGOAL2 <- log(log(1000))
loglogGOAL3 <- log(log(10000))
loglogGOAL4 <- log(log(100000))

# FALL probs 
Fprobs1 <- rep(NA, durations)
Fprobs2 <- rep(NA, durations)
Fprobs3 <- rep(NA, durations)
Fprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL3 +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_interaction * i * loglogGOAL4
	Fprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Fprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Fprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Fprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}

# WINTER probs 
Wprobs1 <- rep(NA, durations)
Wprobs2 <- rep(NA, durations)
Wprobs3 <- rep(NA, durations)
Wprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_winter +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_winter +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL3 +
			b_winter +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_winter +
			b_interaction * i * loglogGOAL4
	Wprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Wprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Wprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Wprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}

# SPRING probs 
Sprobs1 <- rep(NA, durations)
Sprobs2 <- rep(NA, durations)
Sprobs3 <- rep(NA, durations)
Sprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_spring +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_spring +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i +  
			b_logloggoal * loglogGOAL3 +
			b_spring +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_spring +
			b_interaction * i * loglogGOAL4
	Sprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Sprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Sprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Sprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}

# SUMMER probs 
Eprobs1 <- rep(NA, durations)
Eprobs2 <- rep(NA, durations)
Eprobs3 <- rep(NA, durations)
Eprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_summer +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_summer +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i +  
			b_logloggoal * loglogGOAL3 +
			b_summer +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_summer +
			b_interaction * i * loglogGOAL4
	Eprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Eprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Eprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Eprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}
```

``` {r eval=TRUE, echo=FALSE, out.width='70%'}
# VISUALIZATION 
# install-load required packages  
if("ggplot2" %in% rownames(installed.packages()) == FALSE) {
	suppressWarnings(install.packages("ggplot2"))
}
suppressMessages(require(ggplot2))
if("reshape2" %in% rownames(installed.packages()) == FALSE) {
	suppressWarnings(install.packages("reshape2"))
}
suppressMessages(require(reshape2))

# data frame to hold probabilities
dfm <- data.frame(
		"Duration" = 1:92,
		"Fall 100" = Fprobs1,
		"Fall 1,000" = Fprobs2,
		"Fall 10,000" = Fprobs3,
		"Fall 100,000" = Fprobs4,
		"Winter 100" = Wprobs1,
		"Winter 1,000" = Wprobs2,
		"Winter 10,000" = Wprobs3,
		"Winter 100,000" = Wprobs4,
		"Spring 100" = Sprobs1,
		"Spring 1,000" = Sprobs2,
		"Spring 10,000" = Sprobs3,
		"Spring 100,000" = Sprobs4,		
		"Summer 100" = Eprobs1,
		"Summer 1,000" = Eprobs2,
		"Summer 10,000" = Eprobs3,
		"Summer 100,000" = Eprobs4
		)
```


A tidy data frame holds the probabilities ('values' column) and associated categorical variables for a season and a goal amount for plotting. This data frame has 1472 rows = 92 durations \* 4 seasons \* 4 goal amounts chosen for display. Here we see the first change in seasons:

```

```

``` {r eval=TRUE, echo=TRUE, out.width='70%'}
# tidy data frame with factor variables
dfm.melt <- melt(dfm, id = "Duration")		
dfm.melt$Season <- rep(c("Fall", "Winter", "Spring", "Summer"), each = 92*4)
dfm.melt$Goal <- factor(rep(rep(c("$100", "$1,000", "$10,000", "$100,000"), each = 92), 4))
dfm.melt$Goal <- factor(dfm.melt$Goal, levels(dfm.melt$Goal)[c(3,1,2,4)])
dfm.melt <- dfm.melt[,-2]; dfm.melt[366:371, ]
```



``` {r eval=TRUE, echo=FALSE}
ggplot(data=dfm.melt, aes(x=Duration,y=value, color=Season)) +
	geom_line(size=1) + 
	ylim(0,.8) +
	facet_grid(. ~ Goal) +
	theme_bw() +
	ggtitle("Probability of Success by Season and Duration for Four Goals") +
	xlab("Project Duration") +
	ylab(" Probability of Success") +
	labs(color = "Season")
```

```

```

Fall and spring have very similar probabilities so spring over-rides fall in the coloring scheme; both have the highest probabilities. Projects take a dip in the summer, and winter probabilities of success are halfway between fall/spring and summer. 

As previously seen, the highest the goal and duration, the lowest the probability of success, but the rate of decay can be quantified and this plot provides a visualization. The probabilities are somewhat stable for cheaper projects, but take a quicker dip through the more expensive projects in the $10,000s$, and flatten out by the time projects are really expensive. 

It is doubful that shorter projects with a $\$100,000$ goal have a near 40% probability of success, however, so this model needs revision and fine-tuning.


	
---



# Code Appendix

### Data Cleaning and Preparation


``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# load pertinent variables 
ks18 <- read.csv(file = "./kickstarter data/ks-projects-201801.csv", 
                 header = TRUE)[,-c(1:3, 5, 9, 11, 13:15)]

# subset US projects, remove country variable 
us18 <- ks18[ks18$country == "US", -6]

# remove "live" projects (no outcome to base prediction on)
us18 <- us18[us18$state != "live", ]

# convert factors to date variables 
us18$deadline <- as.Date(us18$deadline)  
us18$launched <- as.Date(us18$launched)

# compute duration (project length) variable 
us18$duration <- as.numeric(us18$deadline - us18$launched)

# re-order data 
us18 <- us18[,c(5,4,2,6,3,1)]

# dummy-code outcome variable 'state' to predict success 
us18$state <- ifelse(us18$state == "successful", 1, 0)

# discard senseless date outliers (projects from 1970) 
us18 <- us18[us18$duration < 100, ]

# discard projects under $100 --> gaming the system
us18 <- us18[us18$goal > 99, ]

# transform goal to log(log(goal)) to normalize it for regression 
us18$logloggoal <- log(log(us18$goal))

# dump goal and main_category 
us18 <- us18[, -c(5,6)]
head(us18)
```


``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# recode dates as seasons  
# getSeason function (from 2012 StackOverflow post by Josh O'Brien)
getSeason <- function(DATES) {
    WS <- as.Date("2012-12-21", format = "%Y-%m-%d") # Winter Solstice
    SE <- as.Date("2012-3-21",  format = "%Y-%m-%d") # Spring Equinox
    SS <- as.Date("2012-6-21",  format = "%Y-%m-%d") # Summer Solstice
    FE <- as.Date("2012-9-21",  format = "%Y-%m-%d") # Fall Equinox

    # Convert dates from any year to 2012 dates
    d <- as.Date(strftime(DATES, format="2012-%m-%d"))

    ifelse (d >= WS | d < SE, "Winter",
      ifelse (d >= SE & d < SS, "Spring",
        ifelse (d >= SS & d < FE, "Summer", "Fall")))
}

# pass us18 date variables to getSeason
us18$launched <- getSeason(us18$launched)
us18$deadline <- getSeason(us18$deadline)
head(us18)
```

``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# percentage of different seasons for launched and deadline 
round(nrow(us18[us18$launched != us18$deadline, ])/nrow(us18),4)*100
```


``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# dump 37% of the data with ambiguous seasons 
seasonmatch <- us18[us18$launched == us18$deadline, -2]

# dummies for seasons, base case == Fall 
seasonmatch$winter <- ifelse(seasonmatch$deadline == "Winter", 1, 0)
seasonmatch$spring <- ifelse(seasonmatch$deadline == "Spring", 1, 0)
seasonmatch$summer <- ifelse(seasonmatch$deadline == "Summer", 1, 0)

# dump deadline
seasonmatch <- seasonmatch[, -2]
head(seasonmatch)
```


### Data Analysis 


``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# logistic regression call 
mod1 <- glm(state ~ duration * logloggoal + winter + spring + summer,
			family=binomial, 
			data=seasonmatch)
summary(mod1)
```

``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# a0 = Film & Video project with 0-day duration and $0 logloggoal 
a0 <- coef(mod1)[1] 
b_duration <- coef(mod1)[2]
b_logloggoal <- coef(mod1)[3]
b_winter <- coef(mod1)[4]
b_spring <- coef(mod1)[5]
b_summer <- coef(mod1)[6]
b_interaction <- coef(mod1)[7]


# PREDICTIONS
# initial values for loops 
durations <- 92
loglogGOAL1 <- log(log(100))
loglogGOAL2 <- log(log(1000))
loglogGOAL3 <- log(log(10000))
loglogGOAL4 <- log(log(100000))

# FALL probs 
Fprobs1 <- rep(NA, durations)
Fprobs2 <- rep(NA, durations)
Fprobs3 <- rep(NA, durations)
Fprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL3 +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_interaction * i * loglogGOAL4
	Fprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Fprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Fprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Fprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}

# WINTER probs 
Wprobs1 <- rep(NA, durations)
Wprobs2 <- rep(NA, durations)
Wprobs3 <- rep(NA, durations)
Wprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_winter +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_winter +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL3 +
			b_winter +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_winter +
			b_interaction * i * loglogGOAL4
	Wprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Wprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Wprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Wprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}

# SPRING probs 
Sprobs1 <- rep(NA, durations)
Sprobs2 <- rep(NA, durations)
Sprobs3 <- rep(NA, durations)
Sprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_spring +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_spring +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i +  
			b_logloggoal * loglogGOAL3 +
			b_spring +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_spring +
			b_interaction * i * loglogGOAL4
	Sprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Sprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Sprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Sprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}

# SUMMER probs 
Eprobs1 <- rep(NA, durations)
Eprobs2 <- rep(NA, durations)
Eprobs3 <- rep(NA, durations)
Eprobs4 <- rep(NA, durations)
for (i in 1:durations) {
	regr1 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL1 +
			b_summer +
			b_interaction * i * loglogGOAL1
	regr2 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL2 +
			b_summer +
			b_interaction * i * loglogGOAL2
	regr3 <- a0 + 
			b_duration * i +  
			b_logloggoal * loglogGOAL3 +
			b_summer +
			b_interaction * i * loglogGOAL3
	regr4 <- a0 + 
			b_duration * i + 
			b_logloggoal * loglogGOAL4 +
			b_summer +
			b_interaction * i * loglogGOAL4
	Eprobs1[i] <- unname(exp(regr1)/(1+exp(regr1)))
	Eprobs2[i] <- unname(exp(regr2)/(1+exp(regr2)))
	Eprobs3[i] <- unname(exp(regr3)/(1+exp(regr3)))
	Eprobs4[i] <- unname(exp(regr4)/(1+exp(regr4)))
}
```

``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# VISUALIZATION 
# install-load required packages  
if("ggplot2" %in% rownames(installed.packages()) == FALSE) {
	suppressWarnings(install.packages("ggplot2"))
}
suppressMessages(require(ggplot2))
if("reshape2" %in% rownames(installed.packages()) == FALSE) {
	suppressWarnings(install.packages("reshape2"))
}
suppressMessages(require(reshape2))

# data frame to hold probabilities
dfm <- data.frame(
		"Duration" = 1:92,
		"Fall 100" = Fprobs1,
		"Fall 1,000" = Fprobs2,
		"Fall 10,000" = Fprobs3,
		"Fall 100,000" = Fprobs4,
		"Winter 100" = Wprobs1,
		"Winter 1,000" = Wprobs2,
		"Winter 10,000" = Wprobs3,
		"Winter 100,000" = Wprobs4,
		"Spring 100" = Sprobs1,
		"Spring 1,000" = Sprobs2,
		"Spring 10,000" = Sprobs3,
		"Spring 100,000" = Sprobs4,		
		"Summer 100" = Eprobs1,
		"Summer 1,000" = Eprobs2,
		"Summer 10,000" = Eprobs3,
		"Summer 100,000" = Eprobs4
		)
```


``` {r eval=FALSE, echo=TRUE, out.width='70%'}
# tidy data frame with factor variables
dfm.melt <- melt(dfm, id = "Duration")		
dfm.melt$Season <- rep(c("Fall", "Winter", "Spring", "Summer"), each = 92*4)
dfm.melt$Goal <- factor(rep(rep(c("$100", "$1,000", "$10,000", "$100,000"), 
                                                             each = 92), 4))
dfm.melt$Goal <- factor(dfm.melt$Goal, levels(dfm.melt$Goal)[c(3,1,2,4)])
dfm.melt <- dfm.melt[,-2]
dfm.melt[366:371, ]
```



``` {r eval=FALSE, echo=TRUE, out.width='70%'}
ggplot(data=dfm.melt, aes(x=Duration,y=value, color=Season)) +
	geom_line(size=1) + 
	ylim(0,.8) +
	facet_grid(. ~ Goal) +
	theme_bw() +
	ggtitle("Probability of Success by Season and Duration for Four Goals") +
	xlab("Project Duration") +
	ylab(" Probability of Success") +
	labs(color = "Season")
```


---

